Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2023-11-29 SEIR.tex
Continue edits

@@

>>>>

I transformed parameters with restricted ranges for sampling, to improve efficiency.
Parameters which are constrained to the positive reals ($\sigma_\epsilon$, $\rho$, and $q_c$) were sampled on the log scale.
Parameters which are constrained to the unit interval ($i^+$ and $\vec{\pi}$) were sampled on the logit scale.

@@

This approach provides additional understanding, compared to the approach in \cref{E-backcalc}.
For example, decomposing the change in transmission into changing contacts, $\matr{\kappa}(t)$, changing susceptibility $\vec{s}(t)$, and other unmeasured factors, $\beta(t)$.
By understanding which of these components is changing, policies can be better targeted.
If it is shown that $\beta(t)$ decreases, this implies that for a given amount of activity in the population, there is less transmission.
Such decreases might be beneficial as it allows society to operate in a more normal manner without increasing transmission.
Breaking the trade-off between transmission and activity is desirable because it reduces the disease burden without burdesome restrictions on individuals day-to-day lives.
